Dependency in Refinement Logics

### 2015-10-17 doc/paper.tex
Add some dots

\begin{thm}
  The above rules all define valid tactics:.
  \begin{enumerate}
    \item $\IsTac{\IdTac}$.
    \item $\IsTac{\FailTac}$.
    \item If $\IsTac{\tau_1}$ and $\IsTac{\tau_2}$, then
      $\IsTac{\OrElseTac{\tau_1}{\tau_2}}$.
    \item If $\IsTac{\tau_1}$ and $\IsTac{\tau_2}$, then
      $\IsTac{\ThenTac{\tau_1}{\tau_2}}$.
  \end{enumerate}
\end{thm}
\begin{proof}
  It suffices to verify that the synthesis $E$ of each tactical is well-scoped
  in $\Psi$; in each case, this follows by induction.
  \begin{enumerate}
    \item[(1--2)] Immediate.
    \item[(3)]
      By induction on derivations of
      $\Refine{\JJ}{\OrElseTac{\tau_1}{\tau_1}}{E}{\Psi}$.
      \begin{description}
        \item[Case $\Refine{\JJ}{\tau_1}{\Psi}{E}$] Validity follows from the
          inductive hypothesis $\IsTac{\tau_1}$.
        \item[Case $\NoRefine{\JJ}{\tau_1}$] Validity follows from the
          inductive hypothesis $\IsTac{\tau_2}$.
      \end{description}

>>>>

\begin{thm}
  The above rules all define valid tactics:.
  \begin{enumerate}
    \item $\IsTac{\IdTac}$.
    \item $\IsTac{\FailTac}$.
    \item If $\IsTac{\tau_1}$ and $\IsTac{\tau_2}$, then
      $\IsTac{\OrElseTac{\tau_1}{\tau_2}}$.
    \item If $\IsTac{\tau_1}$ and $\IsTac{\tau_2}$, then
      $\IsTac{\ThenTac{\tau_1}{\tau_2}}$.
  \end{enumerate}
\end{thm}
\begin{proof}
  It suffices to verify that the synthesis $E$ of each tactical is well-scoped
  in $\Psi$; in each case, this follows by induction.
  \begin{enumerate}
    \item[(1--2)] Immediate.
    \item[(3)]
      By induction on derivations of
      $\Refine{\JJ}{\OrElseTac{\tau_1}{\tau_1}}{E}{\Psi}$.
      \begin{description}
        \item[Case $\Refine{\JJ}{\tau_1}{\Psi}{E}$.] Validity follows from the
          inductive hypothesis $\IsTac{\tau_1}$.
        \item[Case $\NoRefine{\JJ}{\tau_1}$.] Validity follows from the
          inductive hypothesis $\IsTac{\tau_2}$.
      \end{description}
